Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
added the digraph for interface paths

>>>>

\begin{figure*}[t]
  \centering
    \includegraphics[width=\textwidth]{../torconfig.png}
    \caption{This flow chart shows all of the possible paths taken through the Tor configuration interface. A state represents a window in the interface, with the exception of the leaves, which indicate the final action taken by the interface (``q'' for quit, ``s'' for success, and ``e'' for error). The transitions between the states indicate which user action causes that transition. The cause for error is can be found \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/torconfig.dot}{here}.}
\end{figure*}
